% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Ilya Arzhannikov}{November 03, 1984}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:iarzhannikov@gmail.com}{iarzhannikov\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{+}7(963)675-44-49\sbull
\href{https://www.linkedin.com/in/%D0%B0%D1%80%D0%B6%D0%B0%D0%BD%D0%BD%D0%B8%D0%BA%D0%BE%D0%B2-%D0%B8%D0%BB%D1%8C%D1%8F-8a125b37/en}{linkedin.com}
\\
Pobedi square 2k1 - 219\sbull
121170\sbull
Moscow\sbull
Russia

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent
I am an experienced and highly skilled C++ software engineer and seek to further develop my skills in a challenging position. I am analytical and methodical with strong problem solving skills, tempered with commercial realism. My primary experience has been working on real-time, multithreaded systems, with a focus on scalability and performance.
\end{multicols}


\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection
  {\href{https://www.artec3d.com/}{Artec 3D}}
  {\textsc{Moscow, Russia}} {%
  \headedsubsection
    {Senior Software Engineer, C++, Artec Studio, 3D scanning SDK.}
    {August \apo15 -- present}
    {\bodytext{Artec Studio is product for 3D scanning and post processing raw data. Artec 3D-scanners have ordered geometry and texture frames on out and Studio helps to build ready models for later using. 3D scanning SDK it's set of routines for scanners communications and post processing algorithm for same goal but without visual component. It is huge projects with a lot of legacy code. My main task is to writing new components, to integrating new 3D-processing algorithms and to refactoring.}\keywords{C++, Visual Studio, Windows, wxWidgets, Qt}}
}

\headedsection
  {\href{https://www.yandex.com/}{Yandex}}
  {\textsc{Yekaterinburg, Russia}} {%
  \headedsubsection
    {Software Engineer, C++, Dynamic crawler.}
    {May \apo14 -- August \apo15}
    {\bodytext{The main point of dynamic crawler is to run JavaScript on html-page for catch AJAX data whichcan’t be downloaded by original crawler. My task is to predict – will there be new data and how much? My part of this system look at new html page that spider have downloaded and give the changes probability. For model fitting I wrote scalable system that crawl Internet, run JS on pages and calculate some aggregations on data. For comparing two pages (html-without-ran-JavaScript and html-with-ran-JavaScript) I made couple of functions. That functions are model answer.}\keywords{C++, Python, Matrixnet, Machine learning, MapReduce, Linux}}
  \headedsubsection
    {Software Engineer, C++, Crawler.}
    {September \apo13 -- May \apo14}
    {\bodytext{I have developed new factors for matrixnet-models. I have done a system for fitting/refitting and deploying matrixnet-models with only one click. Before this there was vary long hand-process for deploying new refitted models with system restarting and so on. Now all refitting-deploying process humanless, take for couple hours and absolutely online.}\keywords{C++, Python, Matrixnet, Machine learning, MapReduce, Linux}}
  \headedsubsection
    {Software Engineer, C++, Mesh project.}
    {May \apo13 -- September \apo13}
    {\bodytext{Mesh is a system like Google Pragel. I have developed cooperative task scheduler on info about available resources (memory, CPU, disk usage). And I have done the system for functional testing.}\keywords{C++, Python, Linux}}
}

\headedsection
  {\href{https://kontur.ru/eng/about}{SKB Kontur}}
  {\textsc{Yekaterinburg, Russia}} {%
  \headedsubsection
    {Software Developer, Erlang, Kontur-Expert.}
    {June \apo11 -- May \apo13}
    {\bodytext{Project for bookkeepers. It allows to estimate financial condition, creditworthiness, the probability of bankruptcy and etc. It was developed with Agile methodology. My zone of responsibility was back end.}\keywords{Erlang, Linux, Agile}}
  \headedsubsection
    {Software Developer, C\#, Kontur-Extern.}
    {July \apo08 -- June \apo11}
    {\bodytext{Kontur-Extern is a huge high-load project for passing any reporting (tax, financial and so on) to public institutions by Internet. I stabilized code, developed new subservices. I did common authentication and authorization system for all SKB Kontur products and did generic index service on Google File System like system.}\keywords{C\#, Windows Server 2003, Windows Server 2008}}
}

\headedsection
  {\href{http://www.rc-spectr.ru/}{Spectr}}
  {\textsc{Yekaterinburg, Russia}} {%
  \headedsubsection
    {Software Developer, C++, 3D engine for automobile- and loco-simulator.}
    {June \apo05 -- July \apo08}
    {\bodytext{I did utilitarian part of 3D engine which includes: editors, import 3DMax models, configuration and calibration of special hardware.}\keywords{C++, Qt, Direct3D, Lua, Linux, Windows}}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Pet projects}

\headedsection
  {\href{http://billijet.ru/}{Billijet}}
  {\textsc{Yekaterinburg, Russia}} {%
  \headedsubsection
    {Software Developer, C++}
    {2012 -- 2013}
    {\bodytext{It would have to be android-cueist. We (I and one more guy) have done prototype that can not move around a table but can detect a boll and hit it. We represented it on \href{http://www.innoprom.com/en/}{INNOPROM} but did not find investors.}\keywords{C++, Qt, OpenCV, Linux, Andurino}}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical spceialties:}
  {Software design and implementation, with(in) a team. Strong knowledge of C++/C\#/Erlang, I use bash and python for automation regularly. Good knowledge of web technology: HTML+CSS, REST \& JavaScript (jQuery).}

\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {Russian \emph{(native)}, English \emph{(intermediate)}.}


\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {}
  {Probability theory, statistics, machine learning, computer vision. Science fiction and fantasy.}

\spacedhrule{1.6em}{-0.4em}

\roottitle{Education}

\headedsection
  {Ural state university.}
  {\textsc{Yekaterinburg, Russia}} {%
  \headedsubsection
    {Mathematics and Mechanics department}
    {Not graduated}
    {\bodytext{}}
}


\end{document}
